%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{ragged2e}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[letterpaper, portrait, margin=1in]{geometry}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\experienceItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\skillItem}[4]{
  \item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1:} #2 & \textbf{#3: } #4
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\experienceSubHeading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1}, \textit{\small #3} & \textit{\small #4} | #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\educationSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\projectItem}[2]{\experienceItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://rozig.github.io/}{\Large Ganzorig Erdenebat}} & \href{https://www.linkedin.com/in/rozig/}{https://www.linkedin.com/in/rozig} \\
  \href{mailto:the.ganzorig25@gmail.com}{the.ganzorig25@gmail.com} | +1 (312) 404-1266 | Mountain View, CA & \href{https://rozig.github.io}{https://rozig.github.io} \\
\end{tabular*}

%-----------SUMMARY-----------------
\section{Summary}
\justify
Result driven software engineer with 6 years of experience specializing in distributed systems and backend systems. Skilled in designing, developing, and optimizing scalable and fault-tolerant solutions for complex infrastructures. 


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeItemListStart
    \experienceSubHeading
      {Mux}{San Francisco, CA}
      {Software Engineer}{May. 2022 - Present}
      \resumeItemListStart
        \experienceItem{Mux Dashboard}
          {Built new features and functionalities for the billing system, such as: 3D Secure verification support for the credit cards, additional analytical instruments to better understand the user conversion rate, multi-tier usage based pricing and cloud marketplace integration (i.e. AWS, GCP, Azure etc). \textit{Technologies used: Elixir, Phoenix, React.js, Exq, Oban, PostgreSQL, CockroachDB, Clickhouse, Redis, AWS, K8s, Bazel, Buildkite.}}
        \experienceItem{Real-Time Video usage API}
          {Built a real-time video usage API, enabling developers to access and understand the usage of the Real-Time video product by collecting usage data from clusters deployed in multi-regions. \textit{Technologies used: Go, gRPC, Protobuf, Kafka, Clickhouse, AWS, K8s, Bazel, Buildkite.}}
      \resumeItemListEnd

    \experienceSubHeading
      {WithMe Health}{San Mateo, CA}
      {Senior Software Engineer}{Feb. 2021 - May. 2022}
      \resumeItemListStart
        % \experienceItem{Cross platform mobile app development}
        %   {Developed and maintained ADA compliant cross-platform applications using React Native, ensuring consistent functionality and user experience across both iOS and Android operating systems. Technologies used: React-Native, Redux, Sendbird, Okta, Split.io, MS AppCenter.}
        \experienceItem{Pharmaceutical guide application}
          {Built new features to support interactions between pharmaceutical guides and patients with instant-messaging, patient call center and assessment system on the React.js web application. \textit{Technologies used: React.js, Redux, Sendbird, AWS Connect, Split.io.}}
        \experienceItem{Microservices}
          {Led the efforts of building and delivering microservices responsible for handling user authentication/authorization, and API gateways for web and mobile applications. \textit{Technologies used: Python, FastAPI, PostgreSQL, Kafka, Kong Gateway, Okta.}}
        \experienceItem{3rd party integration}
          {Led the successful integration of third-party systems (Script Care, Consociate ...) and APIs to further enhance the data ingestion pipeline, enabling seamless data exchange and enhancing functionality. \textit{Technologies used: Python, FastAPI.}}
        \experienceItem{Data ingestion pipeline}
          {Worked on optimization efforts of the ETL pipeline, resulting in improved data processing efficiency, reduced latency, and enhanced scalability that resulted in 33\% faster processing time. \textit{Technologies used: Python, PostgreSQL, Kafka, Elasticsearch, Cassandra, Hazelcast IMDG, Airflow.}}
      \resumeItemListEnd

    \experienceSubHeading
      {WithMe Health}{San Mateo, CA}
      {Software Engineer}{Oct. 2019 - Feb. 2021}
      \resumeItemListStart
        \experienceItem{Data ingestion pipeline}
          {Worked on robust and scalable ETL pipeline, enabling efficient and reliable data acquisition from various sources. \textit{Technologies used: Python, PostgreSQL, Kafka, Elasticsearch, Cassandra.}}
        \experienceItem{Internal framework}
          {Led the development and implementation of an internal framework to streamline software development processes and enhance code reusability across projects which helped to increase the code re-usability by over 50\% through standardized development practices.}
      \resumeItemListEnd

    \experienceSubHeading
      {Genius Plaza Inc.}{Miami, FL}
      {Full-stack Developer}{Aug. 2018 - Sep. 2019}
      \resumeItemListStart
        \experienceItem{Monolith to microservices conversion}
          {Worked on successful conversion of a monolithic system to microservices architecture resulting in improved scalability, maintainability, observability and deployment efficiency. \textit{Technologies used: Python/Django, PostgreSQL, Docker, AWS ECS, AWS RDS, AWS S3, AWS ELB, AWS Route53, AWS CloudWatch, Jenkins.}}
        \experienceItem{Database optimization}
          {Performed database normalization and optimized SQL queries that helped to cut down overall query execution time by 45\%.}
        % \experienceItem{Genius Doctor}
        %   {Developed and maintained responsive and user-friendly web application ensuring seamless user experience across various devices and browsers. Developed and integrated unit and automated testing system into the CI/CD pipline to ensure reliablity of the release. Technologies used: JavaScript, React.js, Redux, Jest/Enzyme, AWS S3, AWS CloudFront, Jenkins, Selenium.}
      \resumeItemListEnd

    % \experienceSubHeading
    %   {Infinite Solutions LLC}{Ulaanbaatar, Mongolia}
    %   {Full-stack Developer}{Jun. 2016 - Nov. 2017}
  \resumeItemListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeItemListStart
    \educationSubheading
      {Maharishi University of Management}{Fairfield, IA}
      {Master of Science in Computer Science;  GPA: 3.80}{Oct. 2017 - Jun. 2020}

    \educationSubheading
      {Mongolian University of Science and Technology}{Ulaanbaatar, Mongolia}
      {Bachelor of Science in Software Engineering;  GPA: 3.46}{Aug. 2013 - Jan. 2017}
  \resumeItemListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeItemListStart
    \skillItem
      {Languages}{Elixir, Python, JavaScript/TypeScript, Go}
      {Frameworks}{Phoenix, Django, Flask, FastAPI}
    \skillItem
      {Web}{React, Redux, CSS3/HTML5/SASS}
      {Web Services}{REST, gRPC, GraphQL}
    \skillItem
      {Databases}{PostgreSQL, Clickhouse, Redis}
      {Other}{Git, K8s, Docker, AWS, GCP, Kafka, Elasticsearch}
  \resumeItemListEnd


%-----------PROJECTS-----------------
% \section{Projects}
%   \resumeItemListStart
%     \projectItem{React.js boilerplate}
%       {Boilerplate project for React.js. Used webpack, styled-components and react-router.}
%     \projectItem{Online Publication Platform}
%       {Clone of Medium.com, built RESTful API and implemented JWT authentication.}
%     \projectItem{Mumagram}
%       {Instagram-like social networking web application for MUM students.}
%     \projectItem{MUMSched}
%       {Academic scheduling web application for MUM students.}
%     \projectItem{Nutrition Calculator}
%       {Nutrition calculator web application on Django (Python).}
%     \projectItem{Logistics System}
%       {Web application for cargo delivery on Django (Python).}
%   \resumeItemListEnd

%-------------------------------------------
\end{document}

